The Two-Column Specht Module of the Hecke Algebra of $S_n$

### 2019-07-06 tex/Crossingless.tex
Added disproof of fibonacci representation

  If $i$ is odd then we have $h(1 + T_i)w = w_1$ and we are done. 
  Otherwise, $h(1 + T_i)w$ is a basis vector with the arc $(i-1,i+2)$ and all other arcs having length 2;
  hence $(1 + T_{i-1})h(1 + T_i)w = w_1$ and we are done.

>>>>

  If $i$ is odd then we have $h(1 + T_i)w = w_1$ and we are done. 
  Otherwise, $h(1 + T_i)w$ is a basis vector with the arc $(i-1,i+2)$ and all other arcs having length 2;
  hence $q^{-1/2}(1 + T_{i-1})h(1 + T_i)w = w_1$ and we are done.
